\toolname: file-based localization of numerical perturbations in data analysis pipelines

### 2020-04-25 paper.tex
update Fig.3 and Fig.1

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. 
\note{The graphs show all executed processes captured by the \reprozip tool
except those that their binaries are placed in directory \texttt{/usr/bin/}. 
We excluded these processes for a better representation of the pipeline execution.}

\begin{figure*}
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.9\linewidth]{figures/p-graph.pdf}
    \caption{Raw provenance graph (\reprozip output), with transient files shown in gray.}
    \label{fig:provenance-graph}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{figures/p-graph-dag.pdf}
    \caption{Provenance DAG, with disambiguated transient files.}
    \label{fig:provenance-dag}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
      \centering
      \includegraphics[width=.7\linewidth]{figures/p-graph-dag-labelled.pdf}
     \caption{Labeled DAG comparing 2 execution conditions, showing 1 non-reproducible process.}
     \label{fig:labeled-dag} 
  \end{subfigure}
    % \includegraphics[width=.8\columnwidth]{figures/provenance-graphs}
    \caption{Provenance graphs
    created from the example pipeline in
    Listing~\ref{listing:sample-script}.
    Processes are represented with circles, files with rectangles, and read/write accesses 
    with plain edges. 
    For visualization purposes, the process tree is represented too, with
    dashed edges. Every node in the graph is labeled using (1) a process id
    created by our reconstruction, (2) the name of the executable run by the
    process or the file name. Process 1 is the initial call to the
    \texttt{sh} interpreter; the other processes are the calls to FSL bet,
    stats and maths made in Listing~\ref{listing:sample-script}. Process 73
    is forked by process 2: it was captured by \reprozip while it did not
    appear in Listing~\ref{listing:sample-script}.
  }
    \label{fig:spot-example}
  \end{figure*}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline.}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}

>>>>

\toolname identifies the components in a pipeline, at the resolution level of a system process, that produce different
results in different execution conditions. First, a directed
bipartite provenance graph is recorded for each pipeline execution, where nodes
represent application processes and files, and edges represent read and
write file accesses (Figure~\ref{fig:provenance-graph}). Second,
transient files, i.e., files that are either deleted during pipeline
execution or modified by multiple processes, are identified and
disambiguated, resulting in a provenance DAG (Directed Acyclic
Graph) in which file nodes have a single parent (in-degree of 1) (Figure~\ref{fig:provenance-dag}). 
DAGs produced in different conditions are then compared, in
a step-by-step execution that prevents the propagation of differences in the pipeline (Figure~\ref{fig:labeled-dag}).
 The resulting labeled graph identifies the
non-reproducible processes in the pipeline. 
\note{Ali}{The graphs show all executed processes captured by the \reprozip tool
except those that their binaries are placed in directory \texttt{/usr/bin/} or \texttt{/bin/}.
We excluded these processes for a better representation of the pipeline execution.}

\begin{figure*}
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.9\linewidth]{figures/p-graph.pdf}
    \caption{Raw provenance graph (\reprozip output), with transient files shown in gray.}
    \label{fig:provenance-graph}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{figures/p-graph-dag.pdf}
    \caption{Provenance DAG, with disambiguated transient files.}
    \label{fig:provenance-dag}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.3\linewidth}
      \centering
      \includegraphics[width=.7\linewidth]{figures/p-graph-dag-labelled.pdf}
     \caption{Labeled DAG comparing 2 execution conditions, showing 1 non-reproducible process.}
     \label{fig:labeled-dag} 
  \end{subfigure}
    % \includegraphics[width=.8\columnwidth]{figures/provenance-graphs}
    \caption{Provenance graphs
    created from the example pipeline in
    Listing~\ref{listing:sample-script}.
    Processes are represented with circles, files with rectangles, and read/write accesses 
    with plain edges. 
    For visualization purposes, the process tree is represented too, with
    dashed edges. Every node in the graph is labeled using the name of the executable run by the
    process or the file name. All the processes are the calls to FSL bet,
    stats and maths made in Listing~\ref{listing:sample-script}. Process \texttt{bet2}
    is forked by process \texttt{bet}: it was captured by \reprozip while it did not
    appear in Listing~\ref{listing:sample-script}.
  }
    \label{fig:spot-example}
  \end{figure*}

@@

\begin{minipage}{\linewidth}
  \centering
    \includegraphics[width=.6\linewidth]{figures/pfs-labeled.pdf} 
    \caption{A complete provenance graph from the PreFreesurfer pipeline.
    We excluded six more processes in the pipeline for better visualization, including:
\texttt{imtest}, \texttt{imcp}, \texttt{remove\_ext}, \texttt{fslval}, \texttt{avscale}, and \texttt{fslhd}.}
    \label{fig:complete_pfs}
\end{minipage}
\end{figure*}
